### 2019-06-25 cv/cv-body.tex
More updating CV

\begin{description}
\tightlist
\item[2019]
Canadian Journal of Fisheries and Aquatic Sciences Stevenson
Lectureship. \url{http://www.nrcresearchpress.com/page/cjfas/award}
\item[2018--20]
Principal Investigator of a two-year grant from Fisheries and Oceans
Canada's Aquatic Climate Change Adaptation Services Program (ACCASP).
Project title: Characterizing range shifts in British Columbia
groundfish species in response to local climate velocities.
\item[2017]
Canadian Society for Ecology and Evolution (CSEE) Early Career Award.\\
\url{http://csee-scee.ca/2017-early-career-awards/}
\item[2015]
David H. Smith Conservation Postdoctoral Research Fellowship\\
\url{http://conbio.org/mini-sites/smith-fellows/meet-the-fellows/2015-fellows/sean-anderson}
\item[2015]
Simon Fraser University Dean of Graduate Studies Convocation Medal\\
\url{https://www.sfu.ca/dean-gradstudies/blog/year/2015/06/SeanAnderson.html}
\item[2014]
Garfield Weston Foundation / BC Packers Ltd.\ Graduate Fellowship in
Marine Sciences
\item[2014]
Graduate Fellowship (two semesters), Simon Fraser University
\item[2012--13]
Canadian Fulbright Scholar award to the University of Washington
\item[2011]
Canadian \href{http://goo.gl/nA1zE}{Governor General's Academic Gold
Medal} for the top-ranked Master's Natural Sciences and Engineering
thesis at Dalhousie University in 2010
\item[2011--14]
Provost Prize of Distinction, Simon Fraser University
\item[2011--14]
Natural Sciences and Engineering Research Council of Canada Postgraduate
Scholarship (Doctoral)
\item[2007--10]
Faculty Research Grant Scholarship, Dalhousie University
\item[2007--09]
Graduate Studies Scholarship, Dalhousie University
\item[2007]
Environmental Programmes Honour Society Medal, Dalhousie University
\end{description}

@@

\begin{description}
\tightlist
\item[2016--17]
NOAA (National Oceanic and Atmospheric Administration) FATE (Fisheries
and the Environment) working group \emph{An early-warning index for
abrupt change in northeast Pacific ecosystems}
\item[2015--16]
NCEAS (National Center for Ecological Analysis and Synthesis, Santa
Barbara, CA) \emph{Applying portfolio effects to the Gulf of Alaska
ecosystem: Did multi-scale diversity buffer against the Exxon Valdez oil
spill?} (\href{https://www.nceas.ucsb.edu/featured/marshall}{URL})
\item[2015--16]
Gordon and Betty Moore Foundation funded working group \emph{Applying
data-limited stock status models and developing management guidance for
unassessed fish stocks}.
\item[2011--13]
NESCent (National Evolutionary Synthesis Center, Durham, NC) Working
Group \emph{Determinants of Extinction in Ancient and Modern Seas} led
by Paul Harnik, Seth Finnegan, and Rowan Lockwood.
(\href{http://www.nescent.org/science/awards_summary.php?id=256}{URL})
\item[2010]
Atlantic Halibut Assessment Science Peer Review Meeting, Fisheries and
Oceans, Dartmouth, NS, Canada.
\item[2007--09]
NCEAS (National Center for Ecological Analysis and Synthesis, Santa
Barbara, CA) Distributed Graduate Seminar, in association with the
Working Group \emph{Finding Common Ground in Marine Conservation and
Management} led by Ray Hilborn and Boris Worm.
(\href{http://www.nceas.ucsb.edu/projects/12307}{URL})
\item[2008]
Workshop on Canadian Science and Management Strategies for Sea Cucumber
(\emph{Cucumaria frondosa}), Fisheries and Oceans, Dartmouth, NS, Canada
(work presented \emph{in absentia}).
\item[2007]
Workshop on Canadian Science and Management Strategies for Atlantic
Hagfish, Fisheries and Oceans, Dartmouth, NS, Canada.
(\href{http://www.dfo-mpo.gc.ca/CSAS/Csas/Publications/Pro-CR/2009/2009_009_e.htm}{URL})
\end{description}

>>>>

\begin{description}
\tightlist
\item[2019]
Canadian Journal of Fisheries and Aquatic Sciences Stevenson
Lectureship. \url{http://www.nrcresearchpress.com/page/cjfas/award} A
``lectureship conferred upon a young, energetic and creative researcher
at the cutting edge of an aquatic discipline''.
\item[2018--20]
Principal Investigator of a two-year grant from Fisheries and Oceans
Canada's Aquatic Climate Change Adaptation Services Program (ACCASP).
Project title: Characterizing range shifts in British Columbia
groundfish species in response to local climate velocities.
\item[2017]
Canadian Society for Ecology and Evolution (CSEE) Early Career Award.\\
\url{http://csee-scee.ca/2017-early-career-awards/}
\item[2015]
David H. Smith Conservation Postdoctoral Research Fellowship\\
\url{http://conbio.org/mini-sites/smith-fellows/meet-the-fellows/2015-fellows/sean-anderson}
\item[2015]
Simon Fraser University Dean of Graduate Studies Convocation Medal\\
\url{https://www.sfu.ca/dean-gradstudies/blog/year/2015/06/SeanAnderson.html}
\item[2014]
Garfield Weston Foundation / BC Packers Ltd.\ Graduate Fellowship in
Marine Sciences
\item[2014]
Graduate Fellowship (two semesters), Simon Fraser University
\item[2012--13]
Canadian Fulbright Scholar award to the University of Washington
\item[2011]
Canadian \href{http://goo.gl/nA1zE}{Governor General's Academic Gold
Medal} for the top-ranked Master's Natural Sciences and Engineering
thesis at Dalhousie University in 2010
\item[2011--14]
Provost Prize of Distinction, Simon Fraser University
\item[2011--14]
Natural Sciences and Engineering Research Council of Canada Postgraduate
Scholarship (Doctoral)
\item[2007--10]
Faculty Research Grant Scholarship, Dalhousie University
\item[2007--09]
Graduate Studies Scholarship, Dalhousie University
\item[2007]
Environmental Programmes Honour Society Medal, Dalhousie University
\end{description}

@@

\begin{description}
\tightlist
\item[2019]
NOAA (National Oceanic and Atmospheric Administration) FATE (Fisheries
and the Environment) working group \emph{Spatial ecosystem state and
pressure indicators and the scale-dependence of temporal indicator
performance in the California Current and beyond}
\item[2018--19]
European Commission Joint Research Council working group \emph{A new
approach to strengthen evidence-based fisheries management}
investigating approaches to providing fisheries management scientific
advice based on model ensembles.
\item[2016--17]
NOAA (National Oceanic and Atmospheric Administration) FATE (Fisheries
and the Environment) working group \emph{An early-warning index for
abrupt change in northeast Pacific ecosystems}
\item[2015--16]
NCEAS (National Center for Ecological Analysis and Synthesis, Santa
Barbara, CA) \emph{Applying portfolio effects to the Gulf of Alaska
ecosystem: Did multi-scale diversity buffer against the Exxon Valdez oil
spill?} (\href{https://www.nceas.ucsb.edu/featured/marshall}{URL})
\item[2015--16]
Gordon and Betty Moore Foundation funded working group \emph{Applying
data-limited stock status models and developing management guidance for
unassessed fish stocks}.
\item[2011--13]
NESCent (National Evolutionary Synthesis Center, Durham, NC) Working
Group \emph{Determinants of Extinction in Ancient and Modern Seas} led
by Paul Harnik, Seth Finnegan, and Rowan Lockwood.
(\href{http://www.nescent.org/science/awards_summary.php?id=256}{URL})
\item[2010]
Atlantic Halibut Assessment Science Peer Review Meeting, Fisheries and
Oceans, Dartmouth, NS, Canada.
\item[2007--09]
NCEAS (National Center for Ecological Analysis and Synthesis, Santa
Barbara, CA) Distributed Graduate Seminar, in association with the
Working Group \emph{Finding Common Ground in Marine Conservation and
Management} led by Ray Hilborn and Boris Worm.
(\href{http://www.nceas.ucsb.edu/projects/12307}{URL})
\item[2008]
Workshop on Canadian Science and Management Strategies for Sea Cucumber
(\emph{Cucumaria frondosa}), Fisheries and Oceans, Dartmouth, NS, Canada
(work presented \emph{in absentia}).
\item[2007]
Workshop on Canadian Science and Management Strategies for Atlantic
Hagfish, Fisheries and Oceans, Dartmouth, NS, Canada.
(\href{http://www.dfo-mpo.gc.ca/CSAS/Csas/Publications/Pro-CR/2009/2009_009_e.htm}{URL})
\end{description}
